Paper

### 2021-12-16 Paper.Rmd
Fixed plot code

ggplot() +
  geom_line(aes(x=1:51, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:51, y=plot_dat[ ,2])) +
  geom_line(aes(x=1:51, y=plot_dat[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected")

>>>>

ggplot() +
  geom_line(aes(x=1:151, y=plot_dat[ ,1]), linetype = 2, color = 'red') +
  geom_line(aes(x=1:151, y=plot_dat[ ,2])) +
  geom_line(aes(x=1:151, y=plot_dat[ ,3]), linetype = 2, color = 'red') + 
  labs(x="Day", y="People infected")
